\documentclass[
    10pt % Default font size, can use 10pt, 11pt or 12pt
]{article}
\usepackage{graphicx}% http://ctan.org/pkg/graphicx
\setlength{\parindent}{0pt}% Remove paragraph indent
\setlength{\parskip}{10pt}
\frenchspacing
\pagestyle{empty}
\begin{document}
%\hspace*{0.5\linewidth}
\begin{minipage}{\linewidth}
W. Ryan Livingston

Somerville, MA

wryanlivingston@gmail.com

+1 330-717-2747

\today
\end{minipage}

% TODO: Explicitly tie my experience to the role

Dear NVIDIA hiring team,

I'm a software engineer with 11 years of experience working in C++ and MATLAB on a source-to-source compiler team. My contributions ranged from enhancing the compiler's runtime libraries to adding new data types like 64-bit integers and sparse matrices to optimization of the generated C/C++ code by integrating the high-performance libraries BLAS and LAPACK. With experience including delivering tested and performant software, leading a team, collaborating with cross-functional teams, learning new skills on the job, and driving product direction I believe I can be an asset to your efforts to deliver performance to your users.

As a senior software engineer, senior team lead, and manager on the MATLAB Coder team at MathWorks, my team and I worked hard to satisfy our users' needs to write MATLAB code, compile it to C++, and deploy their algorithms to standalone hardware while achieving excellent performance. This role gave me direct insight into the needs of scientists and engineers working in their domains. I would love to continue on that path by building tooling that accelerates the workflow and efficiency of your users in the machine learning space.

My background in mathematics, experience working on numerical software, exposure to compiler infrastructure, and an interest in growing my machine learning skills afford me the ability to be an asset to your team at NVIDIA. I appreciate your consideration for an opportunity to interview with you.

All the best,

W. Ryan Livingston

\end{document}
